Modelling last glacial cycle ice dynamics in the Alps

### 2017-07-13 articles/cycle/alps-cycle.tex
Rework surface mass balance subsection.

      The PDD computation accounts for stochastic temperature variations by
      assuming a~normal temperature distribution of standard deviation
      $\sigma$ around the expected value $T_{\mathrm{m}}$. It is expressed
      by an error-function formulation \citep{Calov.Greve.2005},
\begin{align}
&\label{eqn:calovgreve}
    {\text{PDD}} = \int_{t_1}^{t_2} \mathrm{d}t
        \left[\frac{\sigma}{\sqrt{2\pi}}
                \exp\left({-\frac{T_{\mathrm{m}}^2}{2\sigma^2}}\right)
              + \frac{T_{\mathrm{m}}}{2} \, {\text{erfc}}
                \left(-\frac{T_{\mathrm{m}}}{\sqrt{2}\sigma}\right)\right] \,,
\end{align}
      which is numerically approximated using week-long sub-intervals. In
      order to account for the effects of spatial and seasonal variations of
      temperature variability \citep{Seguinot.2013}, $\sigma$ is computed
      from NARR daily temperature values from 1979 to 2000
      \citep{Mesinger.etal.2006}, including variability associated with the
      seasonal cycle, and bilinearly interpolated to the model grids
      (Fig.~\ref{fig:atm}). Degree-day factors for snow and
      ice melt are derived from mass-balance measurements on contemporary
      glaciers from the Coast Mountains and Rocky Mountains in British
      Columbia \citep[Table~\ref{tab:params};][]{Shea.etal.2009}.

>>>>

    The PDD computation accounts for stochastic temperature variations by
    assuming a~normal temperature distribution of standard deviation $\sigma$
    around the expected value $T_{\mathrm{m}}$. It is expressed by an
    error-function formulation \citep{Calov.Greve.2005},
%
\begin{align}
&\label{eqn:calovgreve}
    {\text{PDD}} = \int_{t_1}^{t_2} \mathrm{d}t
        \left[\frac{\sigma}{\sqrt{2\pi}}
                \exp\left({-\frac{T_{\mathrm{m}}^2}{2\sigma^2}}\right)
              + \frac{T_{\mathrm{m}}}{2} \, {\text{erfc}}
                \left(-\frac{T_{\mathrm{m}}}{\sqrt{2}\sigma}\right)\right] \,,
\end{align}
%
    which is numerically approximated using week-long sub-intervals. In
    order to account for the effects of spatial and seasonal variations of
    temperature variability \citep{Seguinot.2013}, $\sigma$ is computed
    from ERA-Interim daily temperature values from 1979 to 2012
    \citep{Mesinger.etal.2006}, including variability associated with the
    seasonal cycle \citep{Seguinot.2013}, and bilinearly interpolated to the
    model grids (Fig.~\ref{fig:inputs}). Degree-day factors for snow and ice
    melt are set to values used in the European Ice Sheet Modelling INiTiative
    \citep[Table~\ref{tab:params}; EISMINT,][]{Huybrechts.1998}.
